TBD

### 2016-10-17 paper.tex
started with LINCAL section

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

\subsection{LINCAL}
Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
Substituting $g_p$ with $e^{\eta_p - i \varphi_p}$, $g_q$ with $e^{\eta_q - i \varphi_q}$ and $y_{\phi_{pq}}$ with $e^{\eta_{\widetilde{\phi}_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}}$ in Eq.~\eqref{eq:vis_red} results in  
\begin{equation}
\label{eq:lincal}
d_{pq} =  e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q} + n_{pq}.
\end{equation}

@@

>>>>

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_red_vec}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

\subsection{LINCAL}

@@

\appendix

\section{LINCAL}
%Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
We can rewrite Eq.~\eqref{eq:vis_red_vec} to
\begin{equation}
\label{eq:lincal_vec}
\bd = \bv(\bvarrho) + \bn, 
\end{equation}
where 
\begin{equation}
\left [ \bv(\bvarrho) \right ]_{\alpha_{pq}} = e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q},
\end{equation}
\begin{equation}
 \bvarrho = 
\begin{bmatrix}
\bmath{\eta} \\
\bvarphi \\
\widetilde{\bmath{\eta}} \\
\widetilde{\bvarphi}
\end{bmatrix},
\end{equation}
with
\begin{align}
 \bmath{\eta} &= [\eta_1, \eta_2,\cdots \eta_N]^T\nonumber\\
 \bmath{\varphi} &= [\varphi_1, \varphi_2,\cdots \varphi_N]^T\nonumber\\
 \widetilde{\bmath{\eta}} &= [\widetilde{\eta_1}, \widetilde{\eta_2},\cdots \widetilde{\eta_L}]^T\nonumber\\
 \widetilde{\bmath{\varphi}} &= [\widetilde{\varphi_1}, \widetilde{\varphi_2},\cdots \widetilde{\varphi_L}]^T.
\end{align}
Moreover, $\bmath{\eta},~\bvarphi,~\widetilde{\bmath{\eta}}$ and $\widetilde{\bvarphi}$ are real valued vectors.
If we Taylor expand Eq.~\eqref{eq:lincal_vec} we obtain
\begin{align}
\bd &= \bv + \Delta \bvarrho \bmJ + \bn\\
\br &= \Delta \bvarrho \bmJ + \bn,
\end{align}
where
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix}
\end{equation}

\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:lincal_definitions}
\end{align}
